Drivers of sex differences in consumption

### 2017-06-01 sex-difference/sex-difference.Rmd
updating sex codes

@@

@@

>>>>

## Diagnosis codes

For COPD, I use the codes recommended by the Chronic Condition Warehouse, but I exclude 490 ("Bronchitis, not specified as acute or chronic") because acute bronchitis seems more common than

@@

icd = read_tsv('../../db/icd/icd.tsv') %>%
  rename(dx_code=code, dx_desc=desc)

sex_icd = read_tsv('sex_codes.tsv', col_types=cols(dx_code='c'))
```

```{r load_dx}
rc_dxs = c('4610', '4619', '462', '4659', '4660', '4739', '486', '490', '7862')
uti_dxs = c('5950', '5959', '5989', '5990', '6235', '7881')

dx = read_tsv(sprintf('../../data/dx/dx_car_claims_%i.tsv', year), col_types=cols(diagnosis='c')) %>%
  select(bene_id=BENE_ID, dx_code=diagnosis)

dx_counts = dx %>% count(dx_code) %>% left_join(icd, by='dx_code') %>% arrange(desc(n))

stopifnot(all(dx_counts$dx_code %in% c(rc_dxs, uti_dxs)))

@@

## Diagnostic codes

For UTIs:

```{r}
sex_icd %>%
  left_join(dx_counts, by='dx_code') %>%
  arrange(dx_group, desc(n)) %>%
  kable
```

For RCs:

```{r}
dx_counts %>% filter(dx_code %in% rc_dxs) %>% kable
```
